The noise-marginalized optimal statistic: A robust hybrid frequentist-Bayesian statistic for the stochastic gravitational-wave background in pulsar timing arrays

### 2018-05-24 manuscript/manuscript.tex
updated results for dipole injection simulations

This overlap between the monopole, dipole, and HD ORFs also means that 
a common red process that does not have HD correlations  
may be confused for a GWB. Figure~\ref{fig:os_dipole} shows the results of 25 simulations 
containing a stochastic signal with dipole spatial correlations. 
Although a dipole signal has been injected, 
the HD ORF gives a mean SNR greater than 5 in 84\% of the simulations. 
However, both the monopole and HD ORFs give smaller values of 
the mean $\hat{A}^2$ and mean SNR compared to the dipole ORF. 
This demonstrates the importance of comparing the SNR from different spatial correlations 
when determining the type of spatial correlations present.
\begin{figure}[t]
	\includegraphics[width=0.9\columnwidth]{plots/optstat_dipole_A5e-15.pdf}
	\caption{Noise-marginalized mean optimal statistic and mean SNR for 25 simulated data sets 
			containing an injected stochastic signal with dipole spatial correlations and $A = 5\times10^{-15}$. 
			We compare the values of the optimal statistic and mean SNR 
			found using monopole (blue), dipole (orange), 
			and HD (green) spatial correlations. 
			The dashed vertical line indicates the injected value, $\hat{A}^2 = 2.5 \times 10^{-29}$.}
	\label{fig:os_dipole}
\end{figure}

>>>>

This overlap between the monopole, dipole, and HD ORFs also means that 
a common red process that does not have HD correlations  
may be confused for a GWB. Figure~\ref{fig:os_dipole} shows the results of 25 simulations 
containing a stochastic signal with dipole spatial correlations. 
Although a dipole signal has been injected, 
the HD ORF gives a mean SNR greater than 5 in 82\% of the simulations. 
However, both the monopole and HD ORFs give smaller values of 
the mean $\hat{A}^2$ and mean SNR compared to the dipole ORF. 
Furthermore, there are no simulations for which the mean SNR with HD ORF 
is greater than the mean SNR with dipole ORF. 
This demonstrates the importance of comparing the SNR from different spatial correlations 
when determining the type of spatial correlations present.
\begin{figure}[t]
	\includegraphics[width=0.9\columnwidth]{plots/optstat_dipole_A5e-15.pdf}
	\caption{Noise-marginalized mean optimal statistic and mean SNR for 25 simulated data sets 
			containing an injected stochastic signal with dipole spatial correlations and $A = 5\times10^{-15}$. 
			We compare the values of the optimal statistic and mean SNR 
			found using monopole (blue), dipole (orange), 
			and HD (green) spatial correlations. 
			The dashed vertical line indicates the injected value, $\hat{A}^2 = 2.5 \times 10^{-29}$.}
	\label{fig:os_dipole}
\end{figure}
